---
title: "Proteomics.data.analysis"
output: github_document
---

<!-- badges: start -->
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

The `Proteomics.data.analysis` package was prepared by the 
MRC Toxicology unit  and Proteomics and
[bioinformaticsfacilities](https://github.com/MRCToxBioinformatics) to 
provide training in the basics of proteomics analyses.
It assume the user's data has been processed by Proteome Discoverer.

Tutorials take the form of vignettes and can be viewed by installing the package 
or navigating to https://mrctoxbioinformatics.github.io/Proteomics_data_analysis/

## Install

```{r, eval=FALSE}
remotes::install_github("MRCToxBioinformatics/Proteomics_data_analysis/", build_vignettes = TRUE)
```

## How to use

Several HTML vignettes are installed with this package which go through how to
use different aspects of the package. You can see a list of available vignettes
with:

```{r, eval=FALSE}
browseVignettes("Proteomics.data.analysis")
```

Or else navigate to https://mrctoxbioinformatics.github.io/Proteomics_data_analysis/
